### 2018-06-11 ident/docs/sifigures.tex
add new figures and remove old ones

@@

@@

\begin{figure}[!tbhp]
	\centering{\includegraphics[width=1.0\textwidth,height=0.3\textheight, keepaspectratio]{figures/figure6/v3_1_2_ck_1_2_parameter_values}}
	\caption{Distribution of predicted parameter values when performing practical identifiability analysis using closed-form solutions for each parameter in flux $v_3$ when the a) and b) Monod-Wyman-Changeaux model for allosteric regulation for $v_3$ is used to generate data, c) and d) experimental data is generated using the Convenience Kinetic rate law model with activation for $v_3$. The left column corresponds to the first root for all three parameters: $V_3^{max}(1)$, $K_3^{fdp}(1)$ and $K_3^{pep}(1)$, and the second column corresponds to the second root of all three parameters in $v_3$: $V_3^{max}(2)$, $K_3^{fdp}(2)$ and $K_3^{pep}(2)$.}\label{fig:parameter_value_v3}
\end{figure}

>>>>

\begin{figure}[!tbhp]
	\centering{\includegraphics[width=1.0\textwidth,height=0.8\textheight, keepaspectratio]{figures/parameter_dist/v3_mwc_ck_parameter_dist}}
	\caption{Distribution of predicted parameter values when performing practical identifiability analysis using closed-form solutions for each parameter in flux $v_3$ when there is no noise in the input experimental data. Here, the data is generated using the MWC model for $v_3$ and the identification is carried out for the Convenience Kinetic model of $v_3$. The top panel shows a violin plot of the distribution of parameter values. The means are indicated by a black line and the median values are indicated by a red line. The bottom panels show the corresponding distributions as histograms. The mismatch between the data and the model used for identification results in large standard deviations for the estimated parameters}\label{fig:v3_mwc_ck_values}
\end{figure}

@@

\begin{figure}[!tbhp]
	\centering{\includegraphics[width=1.0\textwidth,height=0.6\textheight, keepaspectratio]{figures/ident_exp_info/v3_mwc_ck_exp_info}}
	\caption{a) The number of data combination from 21 different in silico experiments that can practically identify each parameter in flux $v_3$ when there is no noise in the input experimental data. Here the data generated using the MWC model for $v_3$ is used to identify parameters in the Convenience Kinetic model of $v_3$. The percentage of total combinations of experimental data used for analysis (3360) that can identify each parameter is also specified. $v_3$ required data from three experiments for analysis. The contribution of different experiment type towards identifying each parameter is shown in the spider plots for b) $V_3^{max}$, c) $K_3^{fdp}$ and d) $K_3^{pep}$. The choice of perturbation chosen for the first experiment (blue) determines the choice of the second (green) and the third perturbation (yellow) required for identifying the parameters.}\label{fig:v3_mwc_ck_ident}
\end{figure}

@@
